Web Service Wrapping, Discovery and Consumption --- More Power to the End-User

### 2010-06-14 trunk/papers/icsoc2010/paper_sec_use_case.tex
checklist at end removed
git-svn-id: https://svn.forge.morfeo-project.org/fast-fp7project@862 d8b0c59b-6544-0410-94d9-83a5658a058e

The intention of this paper was to show the advances made regarding web service discovery and consumption through the two artifacts developed as part of our research. While these artifacts may be deployed and used separately by third-party applications, they were originally developed to form the backbone of the FAST platform. FAST constitutes a novel approach to application composition and business process definition from a top-down user-centric perspective. Therefore, it is aimed to allow users to create their own applications by combining different components, or building blocks, such as graphical forms and back-end services in terms of their inputs and outputs. These two components, as described in Section 3 and 4, are fully integrated and present a high cohesion the rest of the components of the FAST architecture (see Picture~\ref{pic:fast_architecture}.

>>>>

The intention of this paper was to show the advances made regarding web service discovery and consumption through the two artifacts developed as part of our research. While these artifacts may be deployed and used separately by third-party applications, they were originally developed to form the backbone of the FAST platform~\cite{hoyer2009fast}.
FAST constitutes a novel approach to application composition and business process definition from a top-down user-centric perspective. Therefore, it is aimed to allow users to create their own applications by combining different components, or building blocks, such as graphical forms and back-end services in terms of their inputs and outputs. These two components, as described in Section 3 and 4, are fully integrated and present a high cohesion the rest of the components of the FAST architecture (see Picture~\ref{pic:fast_architecture}.
